A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-11-11 sections/queueing_model/proportion_within_target/main.tex
Additional changes based on review
- Reword a sentence
- Move some plots from the main body to the appendix

Figures \ref{fig:markov_vs_des_proportion_comparison_1},
\ref{fig:markov_vs_des_proportion_comparison_2} and 
\ref{fig:markov_vs_des_proportion_comparison_overall} show a comparison of the
mean proportion of individuals within target when using Markov chains and 
discrete event simulation (appendix~\ref{sec:appendix_des}).
The simulation was ran 100 times and the recorded proportions at each iteration 
is used to populate the violin plots.

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/proportion_within_target_comparison/proportion_1.pdf}
    \caption{
        Comparison of proportion within target time for type 1 individuals 
        between values obtained from the Markov chain formulas and values 
        obtained from simulation. 
    }
    \label{fig:markov_vs_des_proportion_comparison_1}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/proportion_within_target_comparison/proportion_2.pdf}
    \caption{
        Comparison of proportion within target time for type 2 individuals 
        between values obtained from the Markov chain formulas and values 
        obtained from simulation. 
    }
    \label{fig:markov_vs_des_proportion_comparison_2}
\end{figure}

>>>>

Figure \ref{fig:markov_vs_des_proportion_comparison_overall} shows a comparison
of the mean proportion of individuals within target when using Markov chains 
and discrete event simulation (appendix~\ref{sec:appendix_des}).
The simulation was ran 100 times and the recorded proportions at each iteration 
is used to populate the violin plots.
The proportions generated by the simulation match the ones generated by the 
Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.

### 2021-11-11 sections/queueing_model/waiting_time/main.tex
Additional changes based on review
- Reword a sentence
- Move some plots from the main body to the appendix

Figures \ref{fig:markov_vs_des_waiting_time_comparison_1},
\ref{fig:markov_vs_des_waiting_time_comparison_2} and
\ref{fig:markov_vs_des_waiting_time_comparison_overall} show a comparison 
between the calculated mean waiting time using Markov chains and the simulated 
waiting time using discrete event simulation over a range of values of 
\(\lambda_2\) (details of the discrete event simulation model are given in 
appendix~\ref{sec:appendix_des}).
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.
For all three plots the waiting times generated by the simulation match the
ones generated by the Markov chains model.

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_1.pdf}
    \caption{
        Comparison of mean waiting time for type 1 individuals between values 
        obtained from the Markov chain formulas and values obtained from 
        simulation.
    }
    \label{fig:markov_vs_des_waiting_time_comparison_1}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_2.pdf}
    \caption{
        Comparison of mean waiting time for type 2 individuals between values 
        obtained from the Markov chain formulas and values obtained from 
        simulation.
    }
    \label{fig:markov_vs_des_waiting_time_comparison_2}
\end{figure}

@@

% TODO: Possibly add another example that will be used in section 5

>>>>

Figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows a 
comparison between the calculated mean waiting time using Markov chains and the
simulated waiting time using discrete event simulation over a range of values of 
\(\lambda_2\) (details of the discrete event simulation model are given in 
appendix~\ref{sec:appendix_des}).
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.
The waiting times generated by the simulation match the ones generated by the 
Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.

@@
